---
title: "glinski_dehydration"
output: html_document
---
tested hypotheses
============
list

things to do
============
list

general configuration
=====================
Install and load supporting libraries.
```{r eval=TRUE, echo=FALSE}
print(Sys.info()[4])

R.Version()$version.string
library(rmarkdown, quietly = TRUE, warn.conflicts = FALSE)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(knitr, quietly = TRUE, warn.conflicts = FALSE)
print("list of loaded packages: ")
print((.packages()))
```

import experimental exposure and dehydration data
=================================
Load csv file with experimental dehydration data. The below may return false but still be OK if rstudio does not have privileges to data directory (e.g., attached drive).

```{r eval=TRUE, echo=FALSE}
if(Sys.info()[4]=="DONNA-PC"){
  dehyd.root <- path.expand("C:/Users/Donna/Documents/Github/glinski_dehydration/")
}

if(Sys.info()[4]=="stp-air-3.local" || Sys.info()[4]=="stp-air.local" || Sys.info()[4]=="stp-air"){
  dehyd.root <- path.expand("~/git/glinski_dehydration/")
}

if(Sys.info()[4]=="DZ2626UTPURUCKE"){
  dehyd.root <- "k:/git/glinski_dehydration/"
}
print(paste("Root directory location: ", dehyd.root, sep=""))

dehyd.csv.in <- paste(dehyd.root, "csv_in/", sep="")
dehyd.csv.out <- paste(dehyd.root, "csv_out/", sep="")
dehyd.graphics <- paste(dehyd.root, "graphics/", sep="")
dehyd.tables <- paste(dehyd.root, "tables/", sep="")

#maybe ok even if remote drive returns false
print(paste("check to see if R can access files OK: ", file.exists(dehyd.csv.in), sep = ""))

#original excel file has some amphibi as matrix instead aof amphib
dehyd <- read.table(paste(dehyd.csv.in,"dehydration2.csv",sep=""), header = TRUE, sep = ",")
```

dehydration exposure data structure
====================================
Check out structure of imported data sets. 

```{r data_structure, eval=TRUE, echo=TRUE}
str(dehyd)
unique(dehyd$parent)
unique(dehyd$analyte)
unique(dehyd$matrix)
unique(dehyd$species)
#View(dehyd)

dehyd.amphib <- dehyd[which(dehyd$matrix=="amphib"),]
dehyd.soil <- dehyd[which(dehyd$matrix=="soil"),]

#atrazine
dehyd.amphib.atrazine <- dehyd.amphib[which(dehyd.amphib$parent=="atrazine"),]
View(dehyd.amphib.atrazine)
dehyd.amphib.atrazine.atrazine <-   dehyd.amphib.atrazine[which(dehyd.amphib.atrazine$analyte=="atrazine"),]
dehyd.amphib.atrazine.dea <-   dehyd.amphib.atrazine[which(dehyd.amphib.atrazine$analyte=="dea"),]
dehyd.amphib.atrazine.dia <-   dehyd.amphib.atrazine[which(dehyd.amphib.atrazine$analyte=="dia"),]
str(dehyd.amphib.atrazine)
dim(dehyd.amphib.atrazine.atrazine)
#create atrazine plus metabolites dataframe
dehyd.amphib.atrazine.atrazineD <- dehyd.amphib.atrazine.atrazine
conc <- aggregate(dehyd.amphib.atrazine$conc, by=list(Category=dehyd.amphib.atrazine$ID), FUN=sum)
dim(conc)
colnames(conc) <- c("ID","conc2")
#View(conc)
#View(cbind(dehyd.amphib.atrazine.atrazineD, conc))
colnames(dehyd.amphib.atrazine.atrazineD)
colnames(conc)
dehyd.amphib.atrazine.atrazineD <- merge(dehyd.amphib.atrazine.atrazineD, conc)
dehyd.amphib.atrazine.atrazineD$analyte <- "atrazineD"
dehyd.amphib.atrazine.atrazineD$conc <- dehyd.amphib.atrazine.atrazineD$conc2
dehyd.amphib.atrazine.atrazineD <- subset(dehyd.amphib.atrazine.atrazineD, select=-c(conc2))
#View(dehyd.amphib.atrazine.atrazineD)

#chlorothalonil
dehyd.amphib.chloro <- dehyd.amphib[which(dehyd.amphib$parent=="chloro"),]
dehyd.amphib.chloro.chloro <- dehyd.amphib.chloro[which(dehyd.amphib.chloro$analyte=="chloro"),]
dehyd.amphib.chloro.chloromet <- dehyd.amphib.chloro[which(dehyd.amphib.chloro$analyte=="chloromet"),]
##chlorothalonil data NA
##create chloro plus metabolites dataframe
#dehyd.amphib.chloro.chloroD <- dehyd.amphib.chloro.chloro
#conc <- aggregate(dehyd.amphib.chloro$conc, by=list(Category=dehyd.amphib.chloro$ID), FUN=sum)
#dim(conc)
#colnames(conc) <- c("ID","conc2")
##View(conc)
##View(cbind(dehyd.amphib.chloro.chloroD, conc))
#colnames(dehyd.amphib.chloro.chloroD)
#colnames(conc)
#dehyd.amphib.chloro.chloroD <- merge(dehyd.amphib.chloro.chloroD, conc)
#dehyd.amphib.chloro.chloroD$analyte <- "chloroD"
#dehyd.amphib.chloro.chloroD$conc <- dehyd.amphib.chloro.chloroD$conc2
#dehyd.amphib.chloro.chloroD <- subset(dehyd.amphib.chloro.chloroD, select=-c(conc2))
##View(dehyd.amphib.chloro.chloroD)

#imidacloprid
dehyd.amphib.imid <- dehyd.amphib[which(dehyd.amphib$parent=="imid"),]
dehyd.amphib.imid.imid <- dehyd.amphib.imid[which(dehyd.amphib.imid$analyte=="imid"),]

#metolachlor
dehyd.amphib.metol <- dehyd.amphib[which(dehyd.amphib$parent=="metol"),]
dehyd.amphib.metol.metol <- dehyd.amphib.metol[which(dehyd.amphib.metol$analyte=="metol"),]
dehyd.amphib.metol.mesa <- dehyd.amphib.metol[which(dehyd.amphib.metol$analyte=="mesa"),]
dehyd.amphib.metol.moxa <- dehyd.amphib.metol[which(dehyd.amphib.metol$analyte=="moxa"),]
#create metol plus metabolites dataframe
dehyd.amphib.metol.metolD <- dehyd.amphib.metol.metol
conc <- aggregate(dehyd.amphib.metol$conc, by=list(Category=dehyd.amphib.metol$ID), FUN=sum)
dim(conc)
colnames(conc) <- c("ID","conc2")
#View(conc)
#View(cbind(dehyd.amphib.metol.metolD, conc))
colnames(dehyd.amphib.metol.metolD)
colnames(conc)
dehyd.amphib.metol.metolD <- merge(dehyd.amphib.metol.metolD, conc)
dehyd.amphib.metol.metolD$analyte <- "metolD"
dehyd.amphib.metol.metolD$conc <- dehyd.amphib.metol.metolD$conc2
dehyd.amphib.metol.metolD <- subset(dehyd.amphib.metol.metolD, select=-c(conc2))
#View(dehyd.amphib.atrazine.atrazineD)

#tridimefon
dehyd.amphib.tdn <- dehyd.amphib[which(dehyd.amphib$parent=="tdn"),]
dehyd.amphib.tdn.tdn <- dehyd.amphib.tdn[which(dehyd.amphib.tdn$analyte=="tdn"),]
dehyd.amphib.tdn.tdla <- dehyd.amphib.tdn[which(dehyd.amphib.tdn$analyte=="tdla"),]
dehyd.amphib.tdn.tdlb <- dehyd.amphib.tdn[which(dehyd.amphib.tdn$analyte=="tdlb"),]
#create tdn plus metabolites dataframe
dehyd.amphib.tdn.tdnD <- dehyd.amphib.tdn.tdn
conc <- aggregate(dehyd.amphib.tdn$conc, by=list(Category=dehyd.amphib.tdn$ID), FUN=sum)
dim(conc)
colnames(conc) <- c("ID","conc2")
#View(conc)
#View(cbind(dehyd.amphib.tdn.tdnD, conc))
colnames(dehyd.amphib.tdn.tdnD)
colnames(conc)
dehyd.amphib.tdn.tdnD <- merge(dehyd.amphib.tdn.tdnD, conc)
dehyd.amphib.tdn.tdnD$analyte <- "tdnD"
dehyd.amphib.tdn.tdnD$conc <- dehyd.amphib.tdn.tdnD$conc2
dehyd.amphib.tdn.tdnD <- subset(dehyd.amphib.tdn.tdnD, select=-c(conc2))
#View(dehyd.amphib.tdn.tdnD)
```

Significance testing.
atrazine. time is significant with a negative slope, opposite what we expected
```{r atrazine_plot, eval=TRUE, echo=TRUE}
print("atrazine")
str(dehyd.amphib.atrazine.atrazine)
time <- dehyd.amphib.atrazine.atrazine$time
conc <- dehyd.amphib.atrazine.atrazine$conc
species <- dehyd.amphib.atrazine.atrazine$species
plot(time, conc)
atrazine.lm <- lm(conc ~ time + species)
summary(atrazine.lm)
```

atrazine+D. time is significant with a negative slope, opposite what we expected
```{r atrazineD_plot, eval=TRUE, echo=TRUE}
print("atrazineD")
str(dehyd.amphib.atrazine.atrazineD)
time <- dehyd.amphib.atrazine.atrazineD$time
conc <- dehyd.amphib.atrazine.atrazineD$conc
species <- dehyd.amphib.atrazine.atrazineD$species
plot(time, conc)
atrazineD.lm <- lm(conc ~ time + species)
summary(atrazineD.lm)
```

chlorothalonil. no concs in data set
```{r chlorothalonil_plot, eval=TRUE, echo=TRUE}
print("chlorothalonil")
#View(dehyd.amphib.chloro.chloro)
str(dehyd.amphib.chloro.chloro)
time <- dehyd.amphib.chloro.chloro$time
conc <- dehyd.amphib.chloro.chloro$conc
species <- dehyd.amphib.chloro.chloro$species
#plot(time, conc)
#chloro.lm <- lm(conc ~ time + species)
#summary(chloro.lm)
```

imidacloprod. 
```{r imidacloprid_plot, eval=TRUE, echo=TRUE}
print("imidacloprid")
#View(dehyd.amphib.imid.imid)
str(dehyd.amphib.imid.imid)
time <- dehyd.amphib.imid.imid$time
conc <- dehyd.amphib.imid.imid$conc
species <- dehyd.amphib.imid.imid$species
plot(time, conc)
#only one species
imid.lm <- lm(conc ~ time) # + species
summary(imid.lm)
```

metolachlor. 
```{r metolachlor_plot, eval=TRUE, echo=TRUE}
print("metolachlor")
#View(dehyd.amphib.imid.imid)
str(dehyd.amphib.metol.metol)
time <- dehyd.amphib.metol.metol$time
conc <- dehyd.amphib.metol.metol$conc
species <- dehyd.amphib.metol.metol$species
plot(time, conc)
#only one species
metol.lm <- lm(conc ~ time + species) # + species
summary(metol.lm)
```

metolachlorD. 
```{r metolachlorD_plot, eval=TRUE, echo=TRUE}
print("metolachlorD")
#View(dehyd.amphib.imid.imid)
str(dehyd.amphib.metol.metolD)
time <- dehyd.amphib.metol.metolD$time
conc <- dehyd.amphib.metol.metolD$conc
species <- dehyd.amphib.metol.metolD$species
plot(time, conc)
#only one species
metolD.lm <- lm(conc ~ time + species) # + species
summary(metolD.lm)
```

triadimefon. 
```{r triadimefon_plot, eval=TRUE, echo=TRUE}
print("triadimefon")
#View(dehyd.amphib.imid.imid)
str(dehyd.amphib.tdn.tdn)
time <- dehyd.amphib.tdn.tdn$time
conc <- dehyd.amphib.tdn.tdn$conc
species <- dehyd.amphib.tdn.tdn$species
plot(time, conc)
#only one species
tdn.lm <- lm(conc ~ time + species)
summary(tdn.lm)
```

triadimefonD. 
```{r triadimefonD_plot, eval=TRUE, echo=TRUE}
print("triadimefonD")
#View(dehyd.amphib.imid.imid)
str(dehyd.amphib.tdn.tdnD)
time <- dehyd.amphib.tdn.tdnD$time
conc <- dehyd.amphib.tdn.tdnD$conc
species <- dehyd.amphib.tdn.tdnD$species
plot(time, conc)
#only one species
tdnD.lm <- lm(conc ~ time + species)
summary(tdnD.lm)
```

test everything together except chlorothalonil, but not summing metabolites
```{r big_test, eval=TRUE, echo=TRUE}
big_test <- rbind(dehyd.amphib.atrazine.atrazine, dehyd.amphib.imid.imid, dehyd.amphib.metol.metol, dehyd.amphib.tdn.tdn)
time <- big_test$time
conc <- big_test$conc
species <- big_test$species
pesticides <- big_test$analyte
plot(time, conc)
big_test.lm <- lm(conc ~ time + species + pesticides)
summary(big_test.lm)
```

test everything together except chlorothalonil, this time summing metabolites
```{r big_test, eval=TRUE, echo=TRUE}
big_test <- rbind(dehyd.amphib.atrazine.atrazineD, dehyd.amphib.imid.imid, dehyd.amphib.metol.metolD, dehyd.amphib.tdn.tdnD)
time <- big_test$time
conc <- big_test$conc
species <- big_test$species
pesticides <- big_test$analyte
plot(time, conc)
big_testD.lm <- lm(conc ~ time + species + pesticides)
summary(big_testD.lm)
```
